plots for paper

### 2019-10-03 src/plots for paper.Rmd
fuck december

```{r pre-install & load packages, include=FALSE}
packages <- c("stringr", "reshape2", "ggplot2", "Hmisc", "viridis", "raster")
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
mthord <- c("mar") #, "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec"

@@

```{r}
mthord <- c("mar") #,  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec"
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

@@

```{r}
z <- subset(y, Depth <510)

bydepth <- ggplot(z, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() + scale_fill_manual(values = probcol) 
plot(bydepth)
```

>>>>

```{r pre-install & load packages, include=FALSE}
packages <- c("stringr", "reshape2", "ggplot2", "Hmisc", "viridis", "raster", "RColorBrewer")
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

```{r}
mthord <- c("mar",  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

@@

```{r}
z <- subset(y, Depth <510)
z <- z[order(z$Depth), ]

y$Depth <- as.factor(y$Depth)
flevels <- levels(y$Depth)
flevels <- rev(flevels)

ggplot(y, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevels, breaks=flevels[seq(1,length(flevels), by = 2)]) + coord_flip()

fuck december
